### 2022-05-06 supplement.Rmd
Make table for selection model analysis

>>>>

```{r, tabs_trimfill_selectionmodels, include=TRUE}
# Format all frequentist results together as a table
map2_dfr(
  c(
    "Two-level random effects model",
    "Trim-and-fill",
    "Selection model: moderate one-tailed",
    "Selection model: severe one-tailed",
    "Selection model: moderate two-tailed",
  "Selection model:severe two-tailed",
  "Selection model: weight-function [0.01,0.05,0.3]"),
    list(
      r_mod,
      res_tf,
      sel_moderateonetailed,
      sel_severeonetailed,
      sel_moderatetwotailed,
      sel_severetwotailed,
      sel_mod),
  function(name, res) {
    print(name)
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      `$SE$` = print_num(res$se),
      `$z$` = print_num(res$zval),
      `$p$` = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95\\% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      bind_rows()
  }
) %>%
  # Rename parameters for readibility
  mutate(
    Parameter = c(
      "Hedges' $g$"
    )
  ) %>%
  # Replace NAs with blank cells
  mutate(across(.fns = ~ ifelse(is.na(.), "", .))) -> tab_freq

# Display the table
apa_table(
  tab_freq,
  align = "llccccc",
  caption = "Sensitivity/robustness analyses frequentist",
  font_size = "scriptsize",
  escape = FALSE
)

# Save the table
write_csv(tab_freq, file = here(tables_dir, "robustness_freq.csv"))
```
